Test susieI using chr17 to 22

### 2020-08-21 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
more parameter examples for susieI

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
tag <- '20200813-1-1'
Niter <- 50
```

@@

@@

# susieI shuffle genes
Shuffle genes to different regions.

Prior change for each iteration:
```{r iter shuffle}
tag <- '20200813-1-1-shuffleg'
load(paste0(outputdir, tag, ".susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

@@

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
mrashdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
tag <- '20200813-1-1'
Niter <- 30
```

@@

## One example

@@

## more examples

Each row represents one simulation run. Runs labeled `1-x` have the same simulation parameters, as you can tell from the true parameters. (and so are runs labled `2-x` and `3-x`)

```{r param}
show_param <- function(tags){
  mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt" )
  param <- do.call(rbind, lapply(mr.ashfs, function(x) t(read.table(x))[2:1,]))

  pars <- cbind(param[seq(1,nrow(param), 2), 1], param[seq(2,nrow(param), 2), 1], param[seq(1,nrow(param), 2), 3], param[seq(2,nrow(param), 2), 3])
  colnames(pars) <- paste(rep(c("pi1.gene_", "pi1.SNP_"), each = 2), c("truth", "mr.ash2"), sep = "")

  susieIfs <- paste0(outputdir, "20200813-", tags, ".susieIres.Rd" )
  param.s <- do.call(rbind, lapply(susieIfs, function(x) {load(x); c(tail(prior.gene_rec, 1), tail(prior.SNP_rec,1))}))

  susieIfs <- paste0(outputdir, "20200813-", tags, ".1.txt")
  param.s.truth <- do.call(rbind, lapply(susieIfs, function(x) {
    a <- read.table(x, header = T);
    c(nrow(a[a$ifcausal == 1 & a$type == "gene", , drop = F])/ nrow(a[a$type == "gene", , drop = F]),
      nrow(a[a$ifcausal == 1 & a$type == "SNP", , drop = F])/ nrow(a[a$type == "SNP", , drop = F]))
    }))

  pars.s <- cbind(param.s.truth, param.s)[, c(1,3,2,4)]
  colnames(pars.s) <-  paste(rep(c("pi1.gene_", "pi1.SNP_"), each = 2), c("susietruth", "susieI"), sep = "")

  df <- cbind(pars, pars.s)
  rownames(df) <- tags

  df %>% 
  kable(format = "html", col.names = colnames(df)) %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")

}

tags <- paste(rep(1:3, each = 5), 1:5, sep ="-")

show_param(tags)
```

# susieI shuffle genes
# one example
Shuffle genes to different regions.

Prior change for each iteration:
```{r iter shuffle}
tag <- '20200813-1-1-shuffleg'
load(paste0(outputdir, tag, ".susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:nrow(df))
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

@@

cat("causal gene fraction:", sum(ngdf$ncausalgene)/sum(ngdf$ngene))
cat("causal snp fraction:", sum(ngdf$ncausalSNP)/sum(ngdf$ns))
